Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-07 doc/icml-presentation/presentation.tex
Updates to the presentation

  \begin{centering}
  \begin{tikzpicture}
    % Tasks.
    \node[style=box] (pos) at (0,0) {\objw{8cm}{%
      \includegraphics[width=\textwidth]{figures/pos.png}\\
      \hfill Part-of-Speech Tagging
      }};
      \node[style=box,below=0.5cm of pos] (dep) {\objw{8cm}{%
      \includegraphics[width=\textwidth]{figures/dep-parse.png}\\
      \hfill Dependency Parsing
      }};
      \node[style=box, below=0.5cm of dep] (act) {\objw{8cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/activity-recognition.png}\\
      \hfill Activity Recognition
      }};

    \node<1->[style=box] (gen) at (6,0) {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Hidden Markov Models
        \item Conditional Random Fields
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    %\node<1->[below=0.5cm of gen-models] (disc) {Discriminative Models};
    \node<2->[style=box,below=1.0cm of gen] (disc) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Max-Entropy Markov Model (Toutanova and Manning, 2000)
        \item Discriminative Parsers (Liang et.\ al, 2006)
        \item Semi-Latent Topic Models (Wang and Mori, 2009)
        \item {\bf Easy to include features and tend to be more accurate.}
      \end{itemize}
      }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/likelihood-em1.png}
    \includegraphics<3-4>[width=\textwidth,height=8cm,keepaspectratio]{figures/likelihood-em2.png}
    \includegraphics<5>[width=\textwidth,height=8cm,keepaspectratio]{figures/likelihood-mom.png}
    \includegraphics<6>[width=\textwidth,height=8cm,keepaspectratio]{figures/likelihood-mom1.png}
      \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
  \end{centering}

  \begin{itemize}
    \item<1-> Log-likelihood function is non-convex.
    \item<4-> This is a problem that doesn't go away even with infinite data.
    \item<5-> Can we build {\bf consistent estimators} that get better with more data?
  \end{itemize}

@@

\begin{frame}
  \frametitle{Spectral Methods}
  \begin{itemize}
    \item Subspace identification [Ljung, 1987]
    \item Observable operator models [Jaeger, 2000]
    \item {\bf Hidden Markov models [Hsu et al, 2009]}
    \item Low-treewidth graphs [Parikh et al., 2012]
    \item Weighted finite state automata [Balle \& Mohri, 2012]
  \end{itemize}
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \note[item]{\todo{Talk about observable operator stuff.}}
\end{frame}

\begin{frame}
  \frametitle{Spectral Methods: Tensor Factorization}
  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1>[style=box] (moments) at (0,0) {\objw{12cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/moments.png}
      }};
    \node<2->[style=box] (moments) at (0,0) {\objw{12cm}{%
      \begin{itemize}
        \item<2-> {\bf Tensor Power Method} for orthonormal $\beta_h$,
          \begin{align*}
            M_3(\beta_h,\beta_h) 
              &= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
              &= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
              &= \pi_{h'} \beta_{h}.
          \end{align*}
        \item<3-> Use $M_2$ to whiten $M_3$.
      \end{itemize}
      }};
    \node<1->[style=box,below=0.1cm of moments]  {\objw{12cm}{%
      \begin{align*}
        \underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
        \underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
        \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
  \end{tikzpicture}
  \end{centering}

@@

\begin{comment}
\begin{frame}
  \frametitle{Spectral Methods for Generative Models.}
  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1-2>[style=box] (pos) at (0,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth]{figures/pos.png}\\
      \hfill Part-of-Speech Tagging
      }};
    \node<3->[style=box] (dep) at (0,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth]{figures/dep-parse.png}\\
      \hfill Dependency Parsing
      }};

    %\node<2-> at (6,0) {Discriminative Models};
    \node<1-2>[style=box] (ahk) at (6,0) {\objw{8cm}{%
      \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/three-view.png}\\
      \begin{itemize}
        \item Solution for multi-view case using tensor factorization (Anandkumar et.\ al, 2012).
        \item<2> HMMs (Anandkumar et.\ al, 2012) 
        \item<2> LDA (Anandkumar et.\ al, 2012) 
      \end{itemize}
      \hfill 
      }};
      \node<3->[style=box] at (6,0) {\objw{8cm}{%
      \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/unmixing.png}\\
      \begin{itemize}
        \item Reduce the problem to multi-view learning via tree-unmixing (Hsu et.\ al, 2012). 
      \end{itemize}
      }};
      \node<4->[style=box] at (4,-3) {\objw{12cm}{%
      {\bf How can we apply these methods for discriminative models?}
      }};
  \end{tikzpicture}
  \end{centering}
  \note[item]{\todo{Talk about observable operator stuff.}}
\end{frame}
\end{comment}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1-10>[style=box] at (0,0) {\obj{%
    {\bf Parameters:} $\pi = [\pi_1, \cdots, \pi_k]$ and $B = [ \beta_1 | \cdots | \beta_k ]$.
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    For a given $x$,
      \begin{itemize}
        \item<3-> $h \in [k] \sim Mult(\pi)$.
        \item<4-> $\epsilon \sim \mathcal{E}$.
        \item<5-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};
    \node<11>[style=box] at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    {\bf Given:} $\mathcal{D} = (x_i, y_i)_{i=1}^{n}$,\\
    can we {\bf estimate parameters} $\pi$ and $B = [ \beta_1 | \cdots | \beta_k ]$?
      }};

    %\node<2-> at (6,0) {Discriminative Models};
    \node[style=box] at (6,0) {\obj{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-1.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-2.png}
    \includegraphics<3-4>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3a.png}
    \includegraphics<5>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3b.png}
    \includegraphics<6>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4a.png}
    \includegraphics<7-8>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4b.png}
    \includegraphics<9>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4c.png}
    \includegraphics<10>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-5.png}
    \includegraphics<11>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-6.png}
      \\{\em Data}
      }};
  \end{tikzpicture}
  \end{centering}

@@

\begin{comment}
\begin{frame}
  \frametitle{Method of Moments.}

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/mom-1.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/mom-2.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/mom-3.png}
      \includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/mom-4.png}
      \includegraphics<5>[width=\textwidth,height=8cm,keepaspectratio]{figures/mom-5.png}
      %\\{\em moment-map}
      }};
      \node<4->[style=box] at (3,-2) {$(\hat m - m^*) \to \normal{0}{\frac{1}{n} \Sigma}$};
      \node<5->[style=box] at (-2,-2) {$(\hat \theta - \theta^*) \to \normal{0}{\frac{1}{n} (\Delta \mathcal{M}^{-1})^T \Sigma \Delta \mathcal{M}^{-1}}$};
  \end{tikzpicture}
  \end{centering}
  %\begin{itemize}
  %  \item<4-> Moments are expected to converge at a $1/\sqrt{n}$ rate, by CLT.
  %  \item<5-> A continuous mapping $\mathcal{M}^{-1}$ will also converge at a $1/\sqrt{n}$ rate.
  %\end{itemize}

    \note[item]{I'm unsure whether this stuff really belongs here.}
    \note[item]{We approach the problem by using the method of moments on three conditional views. }
    \note[item]{Consider a moment map $\mathcal{M}$ that maps the parameters $\theta$ to the moments $m$. For a Gaussian, we have that $\mathcal{M} = (\mu, \sigma^2)$.}
    \note[item]{In general, we will compute the inverse of the moment map to learn the parameters from the sample estimates.}
    \note[item]{By the central limit theorem, our sample estimates of the moments converge at a $1/\sqrt{n}$ rate, so we expect that our parameters will also converge at this rate.}
\end{frame}
\end{comment}

@@

\begin{comment}
\begin{frame}
  \frametitle{Method of Moments for the Mixture of Linear Regressions.}

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{36em}{%
        \begin{align*}
          \action<1->{%
            \E[y] &= \E[\beta_h^T x + \epsilon] \\
                  &= M_1^T \E[x]\\
          }
          \action<2->{%
            \E[y x] &= \E[(\beta_h^T x) x + \epsilon x] \\
              &= M_1^T \E[x\tp{2}]\\
          }
          \action<3->{% 
            \E[y^2] &= \E[(\beta_h^T x)^2 + 2 \epsilon (\beta_h^T x) + \epsilon^2 ] \\
                    &= \E[\trace(\beta_h \beta_h^T x x^T)] + \E[\epsilon^2 ] \\
                    &= \trace(M_2 \E[x\tp{2}]) + \E[\epsilon^2 ] \\
          }
          \action<4->{% 
            \E[y^p x\tp{q}] 
                    &= \trace(M_p \E[x\tp{p+q}]) + \cdots.
          }
        \end{align*}
      }};
  \end{tikzpicture}
  \end{centering}
      \note[item]{In the discriminative case, we do not observe $M_2$ directly from the data, but rather, as we'll see, linear measurements of them.}
      \note[item]{Try to work out the moments for this case and see how they {\tt \#fail} epically.}
\end{frame}
\end{comment}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
            y &= \beta_h^T x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{M_1^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - M_1)^T x + \epsilon}_{\textrm{noise}} \\
          }
          \action<+->{
            y^2 
              &= (\beta_h^T x)^2 + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              &= \trace(\beta_h\tp{2} x\tp{2}) + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              &= \trace(M_2 x\tp{2}) + \E[\epsilon^2] + \trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon \\
              &= \trace(M_2 x\tp{2}) + \underbrace{\E[\epsilon^2]}_{\textrm{bias}} + \underbrace{\trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon}_{\textrm{noise}} \\
          }
          \action<+->{ 
          y^3 &= \innerp{M_3}{x\tp{3}} + \textrm{bias} + \textrm{noise}.
          }
        \end{align*}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] (note) at (0,0) {\objw{12cm}{%
      {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
      }};
    \node[style=box,below=0.1cm of note] {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-1.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-2.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-3.png}
      }};
  \end{tikzpicture}
  \end{centering}
\end{frame}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-2.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-3.png}
      \includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-4.png}
      \includegraphics<5>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-5.png}
      }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{tikzpicture}
    % x, y
    \node<1-4> at (0,0) {%
      \includegraphics<1>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3.png}
      \includegraphics<2->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-em.png}
      };
    % x, y
    \node<1-4> at (6,0) {%
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-spec.png}
      \includegraphics<4->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-specm.png}
      };
      \node<5-> at (0,0) {\objw{12cm}{%
      \begin{small}
  \begin{tabular}{ r r r c c c }
\hline
$b$ & $d$ & $k$ & Spectral & EM & Spectral + EM \\
\hline
  1 & 4 & 2 & 2.45 $\pm$ 3.68 & 0.28 $\pm$ 0.82 & {\bf 0.17 $\pm$ 0.57} \\
  2 & 5 & 2 & 1.38 $\pm$ 0.84 & {\bf 0.00 $\pm$ 0.00} & {\bf 0.00 $\pm$ 0.00} \\
  2 & 5 & 3 & 2.92 $\pm$ 1.71 & 0.43 $\pm$ 1.07 & {\bf 0.31 $\pm$ 1.02} \\
  2 & 6 & 2 & 2.33 $\pm$ 0.67 & 0.63 $\pm$ 1.29 & {\bf 0.01 $\pm$ 0.01} \\
\hline
\end{tabular}
      \end{small}
    }};
  \end{tikzpicture}

  \begin{itemize}
      \item Spectral methods can provide a good initializaton.
  \end{itemize}

    \note[item]{Spectral Experts provides a good initialization to EM.}
    \note[item]{We simulated the performance of spectral experts and compared it to EM.}
    \note[item]{In a non-trivial number of cases, EM did not converge to the right parameters and got stuck in local optima.}
    \note[item]{The parameters estimated by the spectral method were not very good even with $O(10^5)$ samples.}
    \note[item]{However, EM initialized with these parameters did extremely well.}
\note[item]{This finding that spectral methods should be a good initialization for EM is not surprising.}
\note[item]{%
  \begin{itemize}
    \item The biggest sell for spectral methods is that they give a global guarantee on where the parameters are.
    \item The parameters might not be at the global optima, but will hopefully lie in the potential well around it.
    \item EM will then converge to the global optima.
  \end{itemize}
  }
\end{frame}

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
    \item Consistent estimator for the mixture of linear regressions with polynomial sample complexity.
    \item Tackle conditional moments using regression while exploiting structure.
    \item Method of moment estimates can be a good initialization for EM.
  \end{itemize}
\end{frame}

>>>>

  \begin{centering}
  \begin{tikzpicture}
    % Tasks.
    \node[style=box] (gen) at (0,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/gen.png}\\
      \hfill Generative Models
      }};

    \node<1->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<2->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<2->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Logistic Regression
        \item Conditional Random Fields
        \item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

  \end{tikzpicture}
  \end{centering}

  % Really do known Gen (HMMs, ) vs Disc (CRFs) models

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
  \end{centering}

  % Simple message: MLE is consistent but intractable, EM is efficient not but consistent. Can we get something in between.

  \begin{itemize}
    \item<1-> Log-likelihood function is non-convex.
    \item<2-> MLE is consistent but intractable.
    \item<3-> EM is efficient but inconsistent.
    \item<4-> Can we build {\bf efficient yet consistent estimators} that get better with more data?
  \end{itemize}

@@

\begin{frame}
  \frametitle{Spectral Methods}
  \begin{itemize}
     \item Representation Learning
    \begin{itemize}
    \item Subspace identification [Ljung, 1987]
    \item Observable operator models [Jaeger, 2000]
    \item {\bf Hidden Markov models [Hsu et al, 2009]}
    \item Low-treewidth graphs [Parikh et al., 2012]
    \item Weighted finite state automata [Balle \& Mohri, 2012]
  \end{itemize}
     \item<2-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
  \note[item]{\todo{Talk about observable operator stuff.}}
\end{frame}

\begin{frame}
  \frametitle{Spectral Methods via Tensor Factorization}
  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1>[style=box] (moments) at (0,0) {\objw{12cm}{%
      \begin{align*}
        %\underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
        %\underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
        \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1>[style=box,below=0.4cm of moments] {\objw{12cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2>[style=box] (tensorf) at (0,0) {\objw{12cm}{%
      Given orthonormal $\beta_h$,
          \begin{align*}
            M_3(\beta_h,\beta_h) 
              %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
              %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
              &= \pi_{h'} \beta_{h}.
          \end{align*}
      }};

    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
      \hfill {Tensor Power Method}
      }};
  \end{tikzpicture}
  \end{centering}

@@

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1-9>[style=box] at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    {\bf Parameters:} $\pi = [\pi_1, \cdots, \pi_k]$ and $B = [ \beta_1 | \cdots | \beta_k ]$.
    For a given $x$,
      \begin{itemize}
        \item<2-> $h \in [k] \sim Mult(\pi)$.
        \item<3-> $\epsilon \sim \mathcal{E}$.
        \item<4-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};
    \node<10>[style=box] at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    {\bf Given:} $\mathcal{D} = (x_i, y_i)_{i=1}^{n}$,\\
    can we {\bf estimate parameters} $\pi$ and $B = [ \beta_1 | \cdots | \beta_k ]$?
      }};

    %\node<2-> at (6,0) {Discriminative Models};
    \node[style=box] at (6,0) {\obj{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-2.png}
    \includegraphics<2-3>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3a.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3b.png}
    \includegraphics<5>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4a.png}
    \includegraphics<6-7>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4b.png}
    \includegraphics<8>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4c.png}
    \includegraphics<9>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-5.png}
    \includegraphics<10>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-6.png}
      \\{\em Data}
      }};
  \end{tikzpicture}
  \end{centering}

@@

@@

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
          y &= \underbrace{\beta_h^T}_{\textrm{random}} x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{\E[\beta_h]^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - M_1)^T x + \epsilon}_{\textrm{noise}} \\
          }
        \end{align*}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{%
            y &= \underbrace{M_1^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - M_1)^T x + \epsilon}_{\textrm{noise}} \\
            M_1 &= \E[\beta_h] \\
          }
          \action<+->{%
            y^2 
              %&= (\beta_h^T x)^2 + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              %&= \trace(\beta_h\tp{2} x\tp{2}) + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              %&= \trace(M_2 x\tp{2}) + \E[\epsilon^2] + \trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon \\
              &= \trace(M_2 x\tp{2}) + \underbrace{\E[\epsilon^2]}_{\textrm{bias}} + \underbrace{\trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon}_{\textrm{noise}} \\
              M_2 &= \E[\beta_h\tp{2}] \\
          }
          \action<+->{%
          y^3 &= \innerp{M_3}{x\tp{3}} + \textrm{bias} + \textrm{noise} \\
          \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk}.
          }
        \end{align*}
      }};
    \node<4->[style=box,below=0.1cm of measurements]  {\objw{12cm}{%
    We can use \uncover<5->{{\color{blue}{(low-rank)}}} regression to recover $M_p$ from linear measurements.\\
    \uncover<5->{\hfill {\color{blue}{{[Negabhan and Wainwright (2009); Tomioka (2011)]}}}}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}
  \end{centering}

% \begin{frame}
%   \frametitle{Method of Moments for the Mixture of Linear Regressions.}
% 
%   \begin{centering}
%   \begin{tikzpicture}
%     % x, y
%     \node[style=box] (note) at (0,0) {\objw{12cm}{%
%       {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
%       }};
%     \node[style=box,below=0.1cm of note] {\objw{12cm}{%
%       \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-1.png}
%       \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-2.png}
%       \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-3.png}
%       }};
%   \end{tikzpicture}
%   \end{centering}
% \end{frame}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      %\includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-2.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-3.png}
      %\includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-4.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-5.png}
      }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{tikzpicture}
    % x, y
    \node<1-4> (em) at (-3,-0.5) {%
      \includegraphics<1>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3.png}
      \includegraphics<2->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-em.png}
      };
    % x, y
    \node<1-4> at (3,-0.5) {%
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-spec.png}
      \includegraphics<4->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-specm.png}
      };
    \node<5-> at (0,-0.5) {%
      \includegraphics[width=\textwidth,height=5cm,keepaspectratio]{figures/hist.png}
    };

    \node[above=0.1 cm of em] {%
        $y = x + x^4 + x^7 + \epsilon$
    };

%      \begin{small}
%  \begin{tabular}{ r r r c c c }
%\hline
%$b$ & $d$ & $k$ & Spectral & EM & Spectral + EM \\
%\hline
%  1 & 4 & 2 & 2.45 $\pm$ 3.68 & 0.28 $\pm$ 0.82 & {\bf 0.17 $\pm$ 0.57} \\
%  2 & 5 & 2 & 1.38 $\pm$ 0.84 & {\bf 0.00 $\pm$ 0.00} & {\bf 0.00 $\pm$ 0.00} \\
%  2 & 5 & 3 & 2.92 $\pm$ 1.71 & 0.43 $\pm$ 1.07 & {\bf 0.31 $\pm$ 1.02} \\
%  2 & 6 & 2 & 2.33 $\pm$ 0.67 & 0.63 $\pm$ 1.29 & {\bf 0.01 $\pm$ 0.01} \\
%\hline
%\end{tabular}
%      \end{small}
%    }};
  \end{tikzpicture}

  \note[item]{Stable!}
    \note[item]{Spectral Experts provides a good initialization to EM.}
    \note[item]{We simulated the performance of spectral experts and compared it to EM.}
    \note[item]{In a non-trivial number of cases, EM did not converge to the right parameters and got stuck in local optima.}
    \note[item]{The parameters estimated by the spectral method were not very good even with $O(10^5)$ samples.}
    \note[item]{However, EM initialized with these parameters did extremely well.}
\note[item]{This finding that spectral methods should be a good initialization for EM is not surprising.}
\note[item]{%
  \begin{itemize}
    \item The biggest sell for spectral methods is that they give a global guarantee on where the parameters are.
    \item The parameters might not be at the global optima, but will hopefully lie in the potential well around it.
    \item EM will then converge to the global optima.
  \end{itemize}
  }
\end{frame}

  \begin{centering}
  \begin{tikzpicture}
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom1.png}
        \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
  \end{centering}

\end{frame}

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
    \item {\bf Consistent estimator} for the mixture of linear regressions with {\bf polynomial sample and computational complexity}.
    \item<2-> Derive conditional moments using regression.
    \item<3-> Method of moment estimates can be a good initialization for EM.
  \end{itemize}
\end{frame}
